\documentclass[10pt,a4paper,ragged2e]{altacv}

\geometry{left=1.5cm,right=10cm,marginparwidth=7.7cm,marginparsep=0.8cm,top=1.25cm,bottom=1.25cm}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=black,
}

\usepackage[official]{eurosym}


\definecolor{VividPurple}{HTML}{000000}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{2E2E2E}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

%bullets & rating marker
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\begin{document}
\name{Harsh Agrawal}
\tagline{<gym, read, code, sleep, repeat>}
% Add Profile Picture here
% \photo{3.3cm}{profile.jpg}

\personalinfo{
    \email{harshagrawal.1312@gmail.com}
    %   \homepage{harshag.me, cancer-ex.com}
    \linkedin{linkedin.com/in/harshag1312/}
    \github{github.com/harshagrawal13/}
    \twitter{twitter.com/harshag1312}
}

\skillsinfo{
    \code{Python, JS, Java}
}
\begin{fullwidth}
    \makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\footnotesize}


\marginpar{
    \bigskip%
    \vspace*{
        \dimexpr1pt-\baselineskip
    }
    \raggedright{
        \cvsection{Research}
        \cvevent{\textbf{Cancer-eX} - Detecting Pancreatic Cancer early}{}{Aug 2018 - Present}{}
        \begin{itemize}
            \item Researched a subsitute biomarker in saliva to detect Pancreatic and other Gastrointestinal Cancers early via a proposed lateral flow assay-based system targetting the biomarker. This test would be completely non-invasive, point-of-care and nearly 90 times cheaper than the current gold-standard CA19-9 Blood diagnostic test for Pancreatic Cancer.
            \item Designed a simple Risk-assessment tool for Panreatic Cancer using simple etiological factors using their respective relative-risk (RR) values.
        \end{itemize}
        \divider

        \cvsection{Achievements}
        \begin{itemize}
            \cvitem{{Winner, Rise For the World 2020}}{Nov 2021}{Selected as one of the 100 global winners by the Schmidt Foundation. A post-secondary scholarship, an inviation to a residential summit, mentorship is provided under the same.},
            \cvitem{{Bal Shakti Puraskar Recipient 2020}}{Jan 2020}{Highest honor bestowed to an Indian below 18 by the \textbf{President of India} at the Rashtrapati Bhavan.}

            \cvitem{Global Teen Leader 2020}{Jan 2020}{Selected as one of the 35 teens all around the world by Three Dot Dash to participate at the Virtual Just Peace Summit 2020. Was provided with mentorship, guidance along other perks.}

            \cvitem{Gold Medal, Genius Olympiad}{June 2020}{Won gold medal at the category of sciences at one of the largest high-school interdisciplinary competition. It witnessed participation from ~1600 exhibits from ~80 countries.}

            \cvitem{Regeneron ISEF Finalist}{May 2020}{Qualified as one of the 20 team India finalists for ISEF 2020. The competition was cancelled due to the pandemic.}

            \cvitem{Regional Finalist, Google Science Fair}{May 2019}{Selected as one of top 100 exhibits all around the world at the Google Science Fair.}

            \cvitem{Third Award, Spark Teen Accelerator Program}{June 2020}{Won third award globally for our start-up CANCER-EX along with acceptance to their accelerator program.}

            \cvitem{Semi Finalist, Diamond Challenge}{April 2020}{Selected as one of the top 30 teams all around the world for the biggest high-school entrepreneurship competition.}

            \cvitem{Grand Award at IRIS Nationals}{Jan 2020}{Granted in the category of biochemistry at the biggest science fair in the country.}

            \cvitem{CSIR Innovation Award}{Oct 2020}{Highest research-honor bestowed to an Indian under 18 by the Science & Technology Minister of India.}

            \cvitem{Gold Medal at INSEF Nationals}{Jan 2019}{One in five overall winners of the INSEF National fair in the category of biochemistry.}

            \cvitem{First Position, VISION 2030 Challenge}{December 2018}{Winner of the Vision-2030 challenge organized by Techfest IIT Mumbai.}

            \cvitem{First Position, Technatholon Challenge  }{August 2019}{Winner of the Technatholon challenge organized by Techfest IIT Guwahati.}

            \cvitem{Gold Medal, FGSI Science Exhibition}{May 2018}{Awarded for creating a reinforcement-learning based approach to train robots virtually and minimize training losses.}

        \end{itemize}

    }
}

\cvsection{Education}

\cvevent{High School Dimploma}{Bharatiya Vidya Bhavans, Raipur}{April 2013 - May 2021}{}
\begin{itemize}
    \item 10th Grade: 93\%
    \item 12th Grade: 96\%
    \item Subjects: English (99/100), Math(98/100), Biology(91/100), Physics(97/100), Chemistry(92/100), and Computer Science(99/100).
\end{itemize}

\cvsection{Experience}
\cvevent{Lead Data Scientist}{Paraswap.io}{May 2021 - Present}{}
\begin{itemize}
    \item {Paraswap is one of the leading multi-chain Decentralized Exchange Aggregators for cryptocurrencies. I work as a lead data-scientist developing a public dashboard to aggregate Paraswap's statistics such as Users, Volume, and Fees along with other tasks.}
    \item {Public Dashboard: paraswap.io/dashboard}
\end{itemize}
\divider
\cvevent{Founder; Charter President}{Interact Club of Raipur Pinnacle by Rotary}{Jun 2019 - June 2020}{}
\begin{itemize}
    \item {Interact Club of Raipur Pinnacle was founded, under Rotary International, for the means to conduct socio-economic upliftment activities. For the term 2019-2020, we fund-raised ~1500 USD; provided hot and healthy food to 800 locals; distributed clothes and other goods to specially-abled kids alongside conducting a few other activities.}
    \item {For the same, we were recognised with the Platinum Distinction Certification - the highest distinction awarded to a member club by Rotary International.}
\end{itemize}
\divider

\cvevent{President of Indian Chapter}{Elevate the Future}{Apr 2020 - Oct 2020}{}
\begin{itemize}
    \item Elevate The Future Global is an organization created to educate middle and high-school students with subjects such as Entrepreneurship and Computer Science to aid them in their intellectual pursuits.
    \item ETF Chapter India organised two 4-day virtual workshops to teach fundamental and high-level entrepreneurship to ~200 middle and high school students from all across the country.
\end{itemize}
\divider
\cvevent{Hackathon - The Gawler Challenge}{MineNow}{Apr 2020 - Jul 2020}{}
\begin{itemize}
    \item The Gawler Challenge was a global online competition from the Government of South Australia to find mineralization using Machine Learning.
    \item Created three separate machine learning models to predict novel mineralized sites in the Gawler region of South Australia using the existing geo-physical and geo-chemical data-sets. A total of ~300,000 new mineralized points were predicted along with their size and predicted ore/mineral.
\end{itemize}
\divider

\cvevent{Opensource}{}{}{}
\begin{itemize}
    \cvitem{Google Code-In 2018}{}{Completed three tasks for Fedora Project.}

    \cvitem{Getting Hands Dirty with Libp2p}{}{Creating a self-paced, interactive JavaScript workshop for a decentralized peer-to-peer modular system - Libp2p}

    \cvitem{Risk Prediction Web-App}{}{Developed a risk-prediction web-application for Pancreatic Cancer using retrospective relative-risk factors in flask.}

\end{itemize}


\clearpage
% Anything that I add after this page goes to the next page
\end{document}
